A Parallel General Purpose Multi-Objective Optimization Framework, with Application To Electron Beam Dynamics

### 2018-09-29 paper/prab.tex
fixing commas

Particle accelerators play a significant role in many aspects of science and
  technology.
Fields, such as material science, chemistry, the biosciences, particle
  physics, nuclear physics and medicine depend on reliable and effective
  particle accelerators, both as research but as well as practical tools.
Achieving the required performance in the design, commissioning, and operation
  of accelerator facilities is a complex and versatile problem.
Today, tuning machine parameters, e.g., bunch charge, emission time and
  various parameters of beamline elements, is most commonly done manually by
  running simulation codes to scan the parameter space.
This approach is tedious, time consuming and can be error prone.
In order to be able to reliably identify optimal configurations of
  accelerators we propose to solve large multi-objective design optimization
  problems to automate the investigation for an optimal set of tuning
  parameters.
Observe that multiple and conflicting optimality criteria call for a
  multi-objective approach.

@@

Once the shape of the Pareto front has been determined, the buyer can
  \textit{specify preference}, balancing the features by observing the
  effect on the optimality criteria, converging to the preferred solution.
This is called \textit{a posteriori} preference specification since we select
  a solution after all possible trade-offs have been presented to us.
An alternative is to specify preference \textit{a priori}, e.g., by
  weighting (specifying preference before solving the problem) and combining
  all objectives into one and applying a single-objective method to solve the
  problem (yielding only one solution).
In many situations preference is not known \textit{a priori} and an
  \textit{a posteriori} preference specification helps conveying a deeper
  understanding of the solution space.
The Pareto front can be explored and the impact of a trade-off decision then
  becomes visible.

@@

To improve the expressive power of objectives and constraints we introduced a
  simple mechanism to define and call custom functions in expressions.
Using simple functors, e.g., as the one shown in Listing 4 to compute an
  average over a set of data points, enriches expressions with custom
  functions.
Custom function implementations overload the \texttt{()} parenthesis operator.
The function arguments specified in the corresponding expression are stored in
  a \texttt{std::vector} of Boost variants~\cite{boost2} that can be
  booleans, strings or floating point values.

>>>>

Particle accelerators play a significant role in many aspects of science and
  technology.
Fields, such as material science, chemistry, the biosciences, particle
  physics, nuclear physics and medicine depend on reliable and effective
  particle accelerators, both as research but as well as practical tools.
Achieving the required performance in the design, commissioning, and operation
  of accelerator facilities is a complex and versatile problem.
Today, tuning machine parameters, e.g. bunch charge, emission time and
  various parameters of beamline elements, is most commonly done manually by
  running simulation codes to scan the parameter space.
This approach is tedious, time consuming and can be error prone.
In order to be able to reliably identify optimal configurations of
  accelerators we propose to solve large multi-objective design optimization
  problems to automate the investigation for an optimal set of tuning
  parameters.
Observe that multiple and conflicting optimality criteria call for a
  multi-objective approach.

@@

Once the shape of the Pareto front has been determined, the buyer can
  \textit{specify preference}, balancing the features by observing the
  effect on the optimality criteria, converging to the preferred solution.
This is called \textit{a posteriori} preference specification since we select
  a solution after all possible trade-offs have been presented to us.
An alternative is to specify preference \textit{a priori}, e.g. by
  weighting (specifying preference before solving the problem) and combining
  all objectives into one and applying a single-objective method to solve the
  problem (yielding only one solution).
In many situations preference is not known \textit{a priori} and an
  \textit{a posteriori} preference specification helps conveying a deeper
  understanding of the solution space.
The Pareto front can be explored and the impact of a trade-off decision then
  becomes visible.

@@

To improve the expressive power of objectives and constraints we introduced a
  simple mechanism to define and call custom functions in expressions.
Using simple functors, e.g. as the one shown in Listing 4 to compute an
  average over a set of data points, enriches expressions with custom
  functions.
Custom function implementations overload the \texttt{()} parenthesis operator.
The function arguments specified in the corresponding expression are stored in
  a \texttt{std::vector} of Boost variants~\cite{boost2} that can be
  booleans, strings or floating point values.
